%-*-coding:
%presentation(Eng.).tex
%Daily English Presentation
\documentclass[UTF8]{article}

\usepackage{geometry}
\geometry{a4paper,left=3cm,right=3cm,top=1cm,bottom=1cm}
\usepackage{wasysym}

\title{Presentation of Daily Communication English}
\author{First Group}
\date{\today}

\begin{document}
	\maketitle
	Today our group want to show you a interesting experiment in social psychology.
	\section{Introduction}	
	In social psychology,there is a very significant law about "impression" of others:Primacy Effect,also called "First Impression Effect".It means that people will pay more attention to the first information and judge others by it.
	Luchins did such an experiment in 1957. He chose two different small story.The two story describe a piece of life for a elementary school student named Jim.Let us listen to these two stories.
	\section{The First Story}
	Now I begin to tell the first story.
	Jim left home to buy stationery.He walked on the sunny street with two friends,enjoying the full sun.Then he came into the stationery store happily,the store was crowded with people.He was queuing up while chatting with an acquaintance.When he have bought stationery and walked away,he met an acquaintance again.He stopped to greet with his classmates.Later,He said his farewell to friends and went to school.On the way,a girl is walking forward him who had just known by him before the night.They talk a few time and them Jim came to the school.
	\section{The Second Story}
	After school,Jim left the classroom alone and walked out of school. He began to back home on a long road.The sun on the street was so bright that Jim has walked in the cool side of the street.The street he had walked gradually disappeared behind him,he saw the beautiful girl he had met the night before.Jim walked into a candy store,the store was crowded with students,and he saw some familiar faces.Jim waited quietly until he got the attention of the counter attendant to bought a cola.He sat on a chair against the wall and had a drink. He back home after cup was empty.
	\section{Summary}
	After above two stories,what character do you think Jim has?
	The results of the experiment showed that when you tell the first story firstly,78\% of the people considered that Jim was extroverted;When you tell the second story firstly there were only 18\% of people considered that Jim was extroverted.The results show that the sequence of information you received will affects the understanding,and we called it First Cause Effect.
	The reason may be as follows:One is people tend to ignore the information behind,because once people feel that they have enough information to make judgments,they will no longer pay little attention to the subsequent information;Two is most of people think the latter information is often less important than the information at the beginning.
	
	\sun So,may be we are lucky because we are the first group to make the presentation.
\end{document}